The Chemistry Development Kit (CDK) \cdkversion{}: atom typing, depiction, molecular formulas, and substructure searching

### 2017-04-20 article.tex
Update tables and include a "delta" table that provides more comparable times.

\begin{tabular}{lllrclrcll}
Benchmark  & Data Set & Input Format & \multicolumn{3}{c}{CDK 1.4.19} & \multicolumn{3}{c}{CDK \cdkversion{}} & Improvement \\

@@

\multirow{4}{*}{countheavy} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 22.51s   & 113k & 9    & 0.97s & 2.6m & 23.21 \\
                            &                            & 
    SDfile & 0              & 7.21s   & 355k & 25   & 3.75s & 686k & 1.92 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 0              & 8m39.3s  & 193k & 9    & 12.17s & 8.3m & 42.67 \\
                            &                              & 
    SDfile & 0              & 3m17.29s & 510k & 0    & 1m07.23 & 1.5m & 2.93 \\

@@

\multirow{4}{*}{rings -mark} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 22.68   & 112k & 9    & 1.42s & 1.8m & 15.97 \\
                            &                            & 
    SDfile & 0              & 9.36   & 273k  & 0    & 4.37s & 568k & 2.14 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 0              & 8m41.57    & 193k & 9    & 30.58s & 3.3m & 17.06 \\
                            &                              & 
    SDfile & 0              & 4m9.82 & 403k & 0    & 1.20.60s & 1.2m & 3.10 \\

@@

\multirow{4}{*}{rings -sssr} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 27.40s    & 93k & 9    & 1.48s & 1.7m & 18.51 \\
                            &                            & 
    SDfile & 0              & 11.85s    & 216k & 25   & 4.08s & 628k & 2.9 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 0              & 12m4.62s & 138k & 9    & 28.07s & 3.6m & 25.81 \\
                            &                              & 
    SDfile & 0              & 7m09.58s  & 234k & 0    & 1m24.16s & 1.2m & 5.10 \\

@@

\multirow{4}{*}{rings -all} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2126           & 45.28s  & 56k & 26    & 1.27s & 2m & 35.65 \\
                            &                            & 
    SDfile & 16             & 36.56  & 70k & 40   & 4.13s & 620k & 8.85 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 88             & 12m40.20s & 132k & 9    & 26.48s & 3.8m & 28.71 \\
                            &                              & 
    SDfile & 90             & 8m05.64s  & 207k & 0    & 1m18.99s & 1.3m & 6.15 \\

@@

\multirow{4}{*}{cansmi} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 36.58s  & 70k & 9    & 1.83s & 1.4m & 19.99 \\
                            &                            & 
    SDfile & 0              & 21.15s  & 121k & 26   & 4.77s & 537k & 4.43 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 14             & 14m33.86s & 115k & 9    & 42.41s & 2.4m & 20.61 \\
                            &                              & 
    SDfile & 0              & 8m59.82s & 186k & 0    & 1m44.86s & 960k & 5.15 \\

@@

\multirow{4}{*}{convert -ofmt=smi} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 35.63s  & 71k & 9    & 1.37s & 1.9m & 26.01 \\
                            &                            & 
    SDfile & 35             & 20.91s  & 122k & 29   & 4.21s & 608k & 4.97 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 14             & 14m26.02s & 116k & 9    & 28.65s & 3.5m & 30.23 \\
                            &                              & 
    SDfile & 0              & 8m59.38s & 186k & 0    & 1m27.35s & 1.2m & 6.17 \\

@@

\multirow{4}{*}{convert -ofmt=sdf} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 32.42s  & 79k & 9    & 10.33s & 248k & 3.14 \\
                            &                            & 
    SDfile & 13             & 17.00s  & 150k & 29   & 14.49s & 176k & 1.17 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 0              & 14m25.82s & 116k & 9    & 5m30.66s & 304k & 2.62 \\
                            &                              & 
    SDfile & 1              & 8m51.33s & 189k & 0    & 6m50.92s & 245k & 1.29 \\

@@

\multirow{4}{*}{convert -gen2d -ofmt=sdf} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 24m28.02s  & 1.7k & 9    & 35.7s & 72k & 41.12 \\
                            &                            & 
    SDfile & 13             & 35m12.03s  & 1.2k & 29   & 42.08s & 61k & 50.19 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 0              & 3h27m07s  & 8.1k & 9    & 18m02.59s & 93k & 11.48 \\
                            &                              & 
    SDfile & 1              & 5h58m30s  & 4.6k & 0    & 19m54.12s & 84k & 18.01 \\

@@

\multirow{4}{*}{fpgen -type=maccs} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2150           & 1h37m35s  & 438 & 9    & 19.8s & 129k & 295.71 \\
                            &                            & 
    SDfile & 48             & 1h44m17s & 409 & 25   & 22.33s & 114k & 280.21 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 214            & 20h24m57s & 1.4k  & 9    & 13m27.11s & 124k & 91.06 \\
                            &                              & 
    SDfile & 225            & 24h41m46s & 1.1k & 0    & 13m41.83s & 122k & 108.18 \\

@@

\multirow{4}{*}{fpgen -type=path} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & 2112           & 1m14.50s   & 34k & 26    & 8.22s & 312k & 9.06 \\
                            &                            & 
    SDfile & 0              & 1m52.17s   & 23k & 40    & 11.67s & 220k & 9.61 \\
                            & \multirow{2}{*}{ChEMBL 22.1} & 
    SMILES & 0              & 35m02.80s       & 48k & 9    & 5m35.25s & 300k & 6.27 \\
                            &                              & 
    SDfile & 0              & 38m51.73s       & 43k & 0    & 6m7.04s & 274k & 6.35 \\

@@

\multirow{4}{*}{fpgen -type=ecfp4} & \multirow{2}{*}{ChEBI 149}   & 
    SMILES & -              &  N/A        && 9    & 4.47s & 573k & \\
                            &                            & 
    SDfile & -              &  N/A        && 25   & 7.04s & 364k & \\
                            & \multirow{2}{*}{ChEMBL 22.1} &
    SMILES & -              &  N/A        && 9    & 2m45.68s & 608k & \\
                            &                              & 
    SDfile & -              &  N/A        && 0    & 3m59.23s & 421k & \\

@@

>>>>

\begin{tabular}{lllrclrclc}
Benchmark  & \multicolumn{2}{c}{Data Set} & \multicolumn{3}{c}{CDK 1.4.19} & \multicolumn{3}{c}{CDK \cdkversion{}} & Improvement \\

@@

\multirow{4}{*}{countheavy} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 22.51s & 108.2K & 9 & 0.97s & 2.5M & 23.21\\
 &  & sdf & 0 & 7.21s & 355.4K & 25 & 3.75s & 683.3K & 1.92\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 8m39.3s & 193.9K & 9 & 12.17s & 8.3M & 42.67\\
 &  & sdf & 0 & 3m17.29s & 510.4K & 0 & 1m7.23s & 1.5M & 2.93\\

@@

\multirow{4}{*}{rings-mark} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 22.91s & 106.3K & 9 & 1.03s & 2.4M & 22.24\\
 &  & sdf & 0 & 8.71s & 294.2K & 25 & 3.93s & 652K & 2.22\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 8m45.78s & 191.5K & 9 & 17.98s & 5.6M & 29.24\\
 &  & sdf & 0 & 4m12.01s & 399.6K & 0 & 1m14.95s & 1.3M & 3.36\\

@@

\multirow{4}{*}{rings-sssr} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 27.4s & 88.9K & 9 & 1.48s & 1.6M & 18.51\\
 &  & sdf & 0 & 11.84s & 216.4K & 25 & 4.08s & 628K & 2.9\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 12m4.62s & 139K & 9 & 28.07s & 3.6M & 25.81\\
 &  & sdf & 0 & 7m9.58s & 234.4K & 0 & 1m24.16s & 1.2M & 5.1\\

@@

\multirow{4}{*}{rings-all} & \multirow{2}{*}{ChEBI 149} & smi & 2126 & 45.28s & 53.8K & 26 & 1.27s & 1.9M & 35.65\\
 &  & sdf & 16 & 36.56s & 70.1K & 40 & 4.13s & 620.4K & 8.85\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 88 & 12m40.2s & 132.5K & 9 & 26.48s & 3.8M & 28.71\\
 &  & sdf & 90 & 8m5.64s & 207.4K & 0 & 1m18.99s & 1.3M & 6.15\\

@@

\multirow{4}{*}{cansmi} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 36.58s & 66.6K & 9 & 1.83s & 1.3M & 19.99\\
 &  & sdf & 35 & 21.15s & 121.1K & 26 & 4.77s & 537.2K & 4.43\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 14 & 14m33.86s & 115.2K & 9 & 42.41s & 2.4M & 20.61\\
 &  & sdf & 0 & 8m59.82s & 186.6K & 0 & 1m44.86s & 960.4K & 5.15\\

@@

\multirow{4}{*}{convert-ofmtsmi} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 35.63s & 68.4K & 16 & 1.37s & 1.8M & 26.01\\
 &  & sdf & 35 & 20.91s & 122.5K & 29 & 4.21s & 608.6K & 4.97\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 14 & 14m26.02s & 116.3K & 34 & 28.65s & 3.5M & 30.23\\
 &  & sdf & 0 & 8m59.38s & 186.7K & 4 & 1m27.35s & 1.2M & 6.17\\

@@

\multirow{4}{*}{convert-ofmtsdf} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 32.42s & 75.1K & 9 & 10.33s & 235.8K & 3.14\\
 &  & sdf & 13 & 17s & 150.7K & 29 & 14.49s & 176.8K & 1.17\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 14m25.82s & 116.3K & 9 & 5m30.66s & 304.6K & 2.62\\
 &  & sdf & 1 & 8m51.33s & 189.5K & 0 & 6m50.92s & 245.1K & 1.29\\

@@

\multirow{4}{*}{convert--gen2d-ofmtsdf} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 24m28.02s & 1.7K & 9 & 35.7s & 68.2K & 41.12\\
 &  & sdf & 13 & 35m12.03s & 1.2K & 29 & 42.08s & 60.9K & 50.19\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 3h27m7s & 8.1K & 9 & 18m2.59s & 93K & 11.48\\
 &  & sdf & 1 & 5h58m30s & 4.7K & 0 & 19m54.12s & 84.3K & 18.01\\

@@

\multirow{4}{*}{fpgen-type=path} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 1m14.5s & 32.7K & 26 & 8.22s & 296.3K & 9.06\\
 &  & sdf & 0 & 1m52.17s & 22.8K & 40 & 11.67s & 219.6K & 9.61\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & 35m2.8s & 47.9K & 9 & 5m35.25s & 300.4K & 6.27\\
 &  & sdf & 0 & 38m51.73s & 43.2K & 0 & 6m7.04s & 274.4K & 6.35\\

@@

\multirow{4}{*}{fpgen-type=maccs} & \multirow{2}{*}{ChEBI 149} & smi & 2150 & 1h37m35s & 416 & 9 & 19.8s & 123K & 295.71\\
 &  & sdf & 48 & 1h44m17s & 409 & 25 & 22.33s & 114.7K & 280.21\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 214 & 20h24m57s & 1.4K & 9 & 13m27.11s & 124.8K & 91.06\\
 &  & sdf & 225 & 24h41m46s & 1.1K & 0 & 13m41.83s & 122.5K & 108.18\\

@@

\multirow{4}{*}{fpgen-type=circ} & \multirow{2}{*}{ChEBI 149} & smi & 0 & NA & - & 9 & 4.47s & 544.9K & 0\\
 &  & sdf & 0 & NA & - & 25 & 7.04s & 364K & 0\\
 & \multirow{2}{*}{ChEMBL 22.1} & smi & 0 & NA & - & 9 & 2m45.68s & 607.8K & 0\\
 &  & sdf & 0 & NA & - & 0 & 3m59.23s & 420.9K & 0\\

@@

\begin{tabular}{lllrclrcll}
Benchmark  & \multicolumn{2}{c}{Data Set} & \multicolumn{3}{c}{CDK 1.4.19} & \multicolumn{3}{c}{CDK \cdkversion{}} & Improvement \\
           &          &              & Skip & Time & Per Min & Skip  & Time  & Per Min \\
\hline
\multirow{4}{*}{countheavy}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 0s & - & 0 & 0s & - & \\
 &  & sdf & 0 & 0s & - & 0 & 0s & - & \\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 0s & - & 0 & 0s & - & \\
 &  & sdf & 0 & 0s & - & 0 & 0s & - & \\
\hline
\multirow{4}{*}{rings-mark}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 0.4s & 6.1M & 0 & 0.06s & 40.6M & 6.7\\
 &  & sdf & 0 & 1.5s & 1.7M & 0 & 0.18s & 14.2M & 8.3\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 6.48s & 15.5M & 0 & 5.81s & 17.3M & 1.1\\
 &  & sdf & 0 & 54.72s & 1.8M & 0 & 7.72s & 13M & 7.1\\
\hline
\multirow{4}{*}{rings-sssr}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 4.89s & 498.1K & 0 & 0.51s & 4.8M & 9.6\\
 &  & sdf & 0 & 4.63s & 553.4K & 0 & 0.33s & 7.8M & 14\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 3m25.32s & 490.5K & 0 & 15.9s & 6.3M & 12.9\\
 &  & sdf & 0 & 3m52.29s & 433.5K & 0 & 16.93s & 5.9M & 13.7\\
\hline
\multirow{4}{*}{rings-all}  & \multirow{2}{*}{ChEBI 149}  & smi & 14 & 22.77s & 107K & 17 & 0.3s & 8.1M & 75.9\\
 &  & sdf & 16 & 29.35s & 87.3K & 15 & 0.38s & 6.7M & 77.2\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 88 & 4m0.9s & 418K & 0 & 14.31s & 7M & 16.8\\
 &  & sdf & 90 & 4m48.35s & 349.2K & 0 & 11.76s & 8.6M & 24.5\\
\hline
\multirow{4}{*}{cansmi}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 14.07s & 173.1K & 0 & 0.86s & 2.8M & 16.4\\
 &  & sdf & 35 & 13.94s & 183.8K & 1 & 1.02s & 2.5M & 13.7\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 14 & 5m54.56s & 284K & 0 & 30.24s & 3.3M & 11.7\\
 &  & sdf & 0 & 5m42.53s & 294K & 0 & 37.63s & 2.7M & 9.1\\
\hline
\multirow{4}{*}{convert-ofmtsmi}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 13.12s & 185.7K & 7 & 0.4s & 6.1M & 32.8\\
 &  & sdf & 35 & 13.7s & 187K & 4 & 0.46s & 5.6M & 29.8\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 14 & 5m46.72s & 290.4K & 25 & 16.48s & 6.1M & 21\\
 &  & sdf & 0 & 5m42.09s & 294.4K & 4 & 20.12s & 5M & 17\\
\hline
\multirow{4}{*}{convert-ofmtsdf}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 9.91s & 245.8K & 0 & 9.36s & 260.2K & 1.1\\
 &  & sdf & 13 & 9.79s & 261.7K & 4 & 10.74s & 238.6K & 0.9\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 5m46.52s & 290.6K & 0 & 5m18.49s & 316.2K & 1.1\\
 &  & sdf & 1 & 5m34.04s & 301.5K & 0 & 5m43.69s & 293K & 1\\
\hline
\multirow{4}{*}{convert--gen2d-ofmtsdf}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 24m5.51s & 1.7K & 0 & 34.73s & 70.1K & 41.6\\
 &  & sdf & 13 & 35m4.82s & 1.2K & 4 & 38.33s & 66.8K & 54.9\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 3h18m28s & 8.5K & 0 & 17m50.42s & 94.1K & 11.1\\
 &  & sdf & 1 & 5h55m13s & 4.7K & 0 & 18m46.89s & 89.4K & 18.9\\
\hline
\multirow{4}{*}{fpgen-type=path}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 51.99s & 46.9K & 17 & 7.25s & 336K & 7.2\\
 &  & sdf & 0 & 1m44.96s & 24.4K & 15 & 7.92s & 323.5K & 13.3\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 26m23.5s & 63.6K & 0 & 5m23.08s & 311.7K & 4.9\\
 &  & sdf & 0 & 35m34.44s & 47.2K & 0 & 4m59.81s & 335.9K & 7.1\\
\hline
\multirow{4}{*}{fpgen-type=maccs}  & \multirow{2}{*}{ChEBI 149}  & smi & 38 & 1h37m12s & 418 & 0 & 18.83s & 129.4K & 309.7\\
 &  & sdf & 48 & 1h44m10s & 410 & 0 & 18.58s & 137.9K & 336.4\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 214 & 20h16m18s & 1.4K & 0 & 13m14.94s & 126.7K & 91.8\\
 &  & sdf & 225 & 24h38m29s & 1.1K & 0 & 12m34.6s & 133.5K & 117.6\\
\hline
\multirow{4}{*}{fpgen-type=circ}  & \multirow{2}{*}{ChEBI 149}  & smi & -2112 &  & - & 0 & 3.5s & 695.9K & \\
 &  & sdf & 0 &  & - & 0 & 3.29s & 778.8K & \\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 &  & - & 0 & 2m33.51s & 656K & \\
 &  & sdf & 0 &  & - & 0 & 2m52s & 585.5K & \\
\hline
\end{tabular}
